Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-03 journal/article.tex
Fixing todos

The most extreme case of adoption was a big bang transformation. To realize
such a large change it is necessary that the change was centrally coordinated.
For step wise transformations there were three variants depending on the amount
of involvement of management and development teams. In some cases teams played a
passive role, and in some cases management was described to be reluctant to
change. In many cases both management and development dealt with the
transformation on their respective level of influence.

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        Change leaders on other organizational levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Informal spreading of agile awareness  &
                P3, P6, P14, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

The tasks of the change team included first finding an alternative delivery
method to solve problems in the old model [P21, P30]. During the transformation
the team stimulated agile adoption in the organization [P18, P45, P49]. Examples
on their tasks were informing people on the agile model [P4], educating and
coaching [P16, P45, P48, P49], creating an agile cookbook [P23], and organizing
presentations and workshops [P25, P41]. The change team also assessed the
success of transformed teams, and worked for repeating their success across the
organization [P16, P40, P41]. Still one characteristic was that the team was
empowered to act on impediments they discovered [P16, P50].

@@

Leadership for change emerged also on other organizational levels. In many cases
these change leaders were still in management positions [P14, P18, P17]. There
were also agile champions in teams who drove the change on a grassroots level
[P6, P9, P27].
As with higher-ups, these people worked for making agile methods familiar [P2,
P6, P9, P17], making change stick [P2, P18], and persuaded others to use agile
methods [P2, P9, P14].
Benefield [P6] describes that people in teams were well able to adjust the
application of the agile process as they were familiar with the problems at
hands. It was however hard to find people who both understood the agile
principles well, and knew how to coach within the team [P6].
% Also coaches in [P2], and a team in [P16]

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        In-house coaching   &
                P1-P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P18, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 19
        Communities, special interest groups  &
                P3, P6, P7, P9, P10, P11, P12, P14, P32, P41,
                P42, P45, P47, P52  \\   % 14 
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.35\textwidth}
                     >{\raggedright\arraybackslash}p{0.57\textwidth} }
        \toprule
        Investments during transformation      &  Described in  \\
        \midrule
        Using external consultants  &
                P5-P9, P16-P21, P23 P25, P27, P29-P31,
                P34, P35, P37-P41, P44, P46, P47, P50, P51  \\  % 29
        New project management tools for agile  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Continuous builds and testing  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments done during transformation, aiming to make
             agile methods perform better}
    \label{table:transformation_investments}
\end{table}

@@

When a general problem of frequent broken builds existed it was easy to acquire a
buy in for creating an organization-wide standard for automating builds and
tests [P11]. On the other hand, many cases emphasized that building the
continuous integration environment required a significant investment [P17, P34,
P42]. In order to have the focus and resources for creating a proper integration
environment a dedicated team was Some organizations appointed a dedicated team
to ensure the focus and resources for creating a proper integration environment
were available [P5, P16, P17].

@@

\subsubsection{Other issues in large organizations}

In addition to inter-team coordination there were also other challenges that
should only emerge in a sizable organization.
Additional layers of management are usually necessary to steer large groups of
people, but agile methods provide little guidance on how to organize management.
Problems may arise in a large environment if the schedule of agile adoption
varies from team to team. Internal fragmentation is a further problem that may
be encountered in large organizations.
Table \label{table:challenges_largescale} summarizes these challenges.

@@

>>>>

The most extreme case of adoption was a big bang transformation. To realize such
a large change it is necessary that the change was centrally coordinated.
For step wise transformations the the amount of management and development team
involvement varied. At one extreme, the change was lead by management while
teams played a passive role. At the other end management was described to be
reluctant to change while teams pushed for change. Many cases took a middle
course where both management and development dealt with the transformation on
their respective level of influence.

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Change leaders         &  Described in  \\
        \midrule
        High-up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Agile task group for coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        Change leaders on development team levels  &
                P2, P6, P9, P14, P17, P18, P27  \\
        Informal spreading of agile awareness  &
                P3, P6, P14, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of entities leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

The typical first task of the change team was to decide on an alternative
delivery method to solve problems in the old model [P21, P30]. During the
transformation the team stimulated agile adoption in the organization [P18, P45,
P49]. Other examples on thechange team's tasks were informing people on the
agile model [P4], educating and coaching [P16, P45, P48, P49], creating an agile
cookbook [P23], and organizing presentations and workshops [P25, P41]. The
change team also assessed the success of transformed teams, and worked for
repeating their success across the organization [P16, P40, P41]. The change team
was empowered to act on removing impediments they discovered [P16, P50].

@@

Beyond executive positions, leadership for change emerged also on lower
organizational levels. In many cases these change leaders were still in
management positions [P14, P18, P17]. There were also agile champions in teams
who drove the change on a grassroots level [P6, P9, P27].
As with higher-ups, these people worked for making agile methods familiar [P2,
P6, P9, P17], making change stick [P2, P18], and persuaded others to use agile
methods [P2, P9, P14].
Benefield [P6] describes that people in teams were well able to adjust the
application of the agile process as they were familiar with the problems at
hands. It was however hard to find people who both understood the agile
principles well, and knew how to coach within the team [P6].
% Also coaches in [P2], and a team in [P16]

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
%         In-house coaching   &
%                 P1-P3, P6, P11, P16, P23, P29, P31, P32,
%                 P39, P41, P45, P47, P49, P50, P52  \\    % 17
        Seminars and workshops   &
                P1-P4, P7, P9, P10, P18, P11, P16, P23, P25,
                P26, P27, P32, P41, P44, P46, P47   \\   % 19
        Communities, special interest groups  &
                P3, P6, P7, P9, P10, P11, P12, P14, P32, P41,
                P42, P45, P47, P52  \\   % 14 
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.35\textwidth}
                     >{\raggedright\arraybackslash}p{0.57\textwidth} }
        \toprule
        Investments during transformation      &  Described in  \\
        \midrule
        Using external consultants  &
                P5-P9, P16-P21, P23 P25, P27, P29-P31,
                P34, P35, P37-P41, P44, P46, P47, P50, P51  \\  % 29
        New project management tools for agile  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Creating a continuous build and integration system  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments done during transformation, aiming to make
             agile methods perform better}
    \label{table:transformation_investments}
\end{table}

@@

When a general problem of frequent broken builds existed it was easy to acquire
a buy in for creating an organization-wide standard for automating builds and
tests [P11]. On the other hand, many cases emphasized that building a continuous
integration environment required a significant investment [P17, P34, P42].
In order to have the focus and resources for creating a proper integration
environment a dedicated team was created. Having an integration team ensured
that focus and resources were available for creating a proper integration
environment [P5, P16, P17].

@@

\subsubsection{Issues specific to large organizations}

In addition to inter-team coordination there were also other challenges that
should only emerge in a sizable organization.
Most importantly, additional layers of management are usually necessary to steer
large groups of people. The problem is that agile methods provide little
guidance on how to organize management.
Problems may also arise in a large environment if the schedule of agile adoption
varies from team to team. Internal fragmentation is a further problem that may
be encountered in large organizations.
Table \label{table:challenges_largescale} summarizes these challenges.

@@

TODO:
* Mieti rakenne
* Mieti onko seuraava ``other than development'' hyvä otsikko
